\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[letterpaper, margin=0.5in, bottom=0.75in, top=0.5in]{geometry}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[dvipsnames]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

% Custom Month-Year command
\newcommand{\monthyear}{%
  \ifcase\month\or January\or February\or March\or April\or May\or June\or July\or August\or September\or October\or November\or December\fi \space \number\year
}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - Balanced
\titleformat{\section}{
  \vspace{-5pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\hrule \vspace{-3pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{0pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{\linewidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \small #2 \hspace{1pt}\faCalendar* \\
      \textit{\small#3} & \small \textit{#4} \hspace{1pt}\faMapMarker* \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \small #2 \hspace{1pt}\faCalendar* \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}, itemsep=2pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.20in, itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\hfill \textcolor{gray}{\small \textit{Last updated in \monthyear \hspace{1pt} \faHistory}}

\vspace{-15pt}

\begin{center}
    {\Huge \scshape Ahmed Fouad Lagha} \\ \vspace{5pt}
    \textbf{\Large PhD Researcher @ ELTE $|$ Data Science \& ML} \\ \vspace{5pt}
    \small 
    \faMapMarker* \hspace{0.5pt} Budapest, Hungary \hspace{5pt} $|$ \hspace{5pt}
    \faPhone \hspace{0.5pt} (+36) 20 425 52 \hspace{5pt} $|$ \hspace{5pt}
    \faEnvelope \hspace{0.5pt} \href{mailto:ahmed.lagha@inf.elte.hu}{\underline{ahmed.lagha@inf.elte.hu}} \\ \vspace{3pt}
    \faLinkedin \hspace{0.5pt} \href{https://linkedin.com/in/ahmed-fouad-lagha}{\underline{linkedin.com/in/ahmed-fouad-lagha}} \hspace{3pt} $|$ \hspace{3pt}
    \faGithub \hspace{0.5pt} \href{https://github.com/ahmed-fouad-lagha}{\underline{github.com/ahmed-fouad-lagha}} \hspace{3pt} $|$ \hspace{3pt}
    \faGlobe \hspace{0.5pt} \href{https://ahmed-fouad-lagha.github.io/}{\underline{ahmed-fouad-lagha.github.io}}
\end{center}

\vspace{-15pt}

\section{Summary}
 {
  Dedicated PhD Researcher specializing in Privacy-Preserving Machine Learning and Data Science. Proven track record in developing state-of-the-art Deep Learning models and implementing secure AI systems using Federated Learning and Differential Privacy. Experienced in software engineering with a strong background in architecting scalable web applications and LLM-based orchestration pipelines. Committed to advancing the frontier of secure and trustworthy artificial intelligence.
 }

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Teaching Assistant}{Feb. 2026 -- Jun. 2026}
      {Eötvös Loránd University (ELTE)}{Budapest, Hungary}
      \resumeItemListStart
        \resumeItem{Designed practical labs focusing on Adversarial Machine Learning and Privacy-Preserving AI using PyTorch.}
        \resumeItem{Guided students through the implementation of state-of-the-art attacks, including Evasion (FGSM, PGD), Data Poisoning (Backdoors), and Membership Inference.}
        \resumeItem{Mentored students on defensive strategies like Differential Privacy (DP-SGD), Federated Learning, and Adversarial Training. Course Link: \href{https://elte-dsed.github.io/Intro-Data-Security/}{\underline{HERE}}}
      \resumeItemListEnd

    \resumeSubheading
      {PhD Researcher (Privacy-Preserving ML)}{Sep. 2025 -- Present}
      {Eötvös Loránd University (ELTE)}{Budapest, Hungary}
      \resumeItemListStart
        \resumeItem{Implemented federated training flows and applied Differential Privacy techniques for synthetic data generation.}
        \resumeItem{Built evaluation pipelines to quantify privacy--utility tradeoffs and documented results demonstrating improved privacy guarantees with acceptable predictive performance.}
        \resumeItem{Awarded the Stipendium Hungaricum Scholarship based on academic excellence and research potential.}
      \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{Jun. 2023 -- Feb. 2025}
      {ALX Africa}{Remote}
      \resumeItemListStart
        \resumeItem{Developed design systems and analyzed project limitations, performance requirements, and interfaces to streamline development.}
        \resumeItem{Modeled applications and system architectures to assist developers in writing efficient and maintainable code.}
        \resumeItem{Evaluated system capabilities and requirements through data manipulation, storage, and retrieval optimization.}
        \resumeItem{Collaborated in a remote environment, utilizing project management and creative problem-solving skills to meet technical objectives.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{MyVellum} \href{https://myvellum.me}{\faGlobe} $|$ \emph{LLM Orchestration, RAG, Docker, CI/CD}}{Dec. 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Designed and implemented LLM orchestration and modular prompt templates to standardize model usage across product teams.}
            \resumeItem{Built vector-backed RAG pipelines and context-stitching services to ground model responses and reduce hallucinations in production.}
            \resumeItem{Integrated automated evaluation gates into CI/CD to track relevance and safety metrics for model updates.}
            \resumeItem{Owned API design and Docker-based deployment pipelines; mentored two engineers in prompt engineering and testing best practices.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{RayaneBio E-Commerce Platform} \href{https://www.rayanebio.social/}{\faGlobe} $|$ \emph{React, Next.js, HTML, CSS}}{Dec. 2024 -- Mar. 2025}
          \resumeItemListStart
            \resumeItem{Architected and deployed a responsive e-commerce platform for organic products resulting in seamless user experiences and increased client satisfaction.}
            \resumeItem{Implemented advanced product display, secure user authentication, and intuitive navigation features, enhancing customer engagement through integrated testimonials.}
            \resumeItem{Designed and showcased company values and customer testimonials, driving brand loyalty and positive user feedback.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Discretuna Text Summarizer} \href{https://github.com/ahmed-fouad-lagha/discretuna-summarizer}{\faGithub} $|$ \emph{Python, Flask, NLTK, scikit-learn, HTML, CSS}}{May 2025}
          \resumeItemListStart
            \resumeItem{Developed a web application for automatic text summarization using the Discrete Tuna Optimization (DTO) algorithm.}
            \resumeItem{Implemented features for text input/file upload and adjustable summarization parameters.}
            \resumeItem{Provided statistical analysis of summary quality, including ROUGE score and readability metrics.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{E-Learning Platform} \href{https://github.com/ahmed-fouad-lagha/E-Learning_Platform}{\faGithub} $|$ \emph{Node.js, Express.js, MongoDB, React, Redux, SCSS}}{Jul. 2025}
          \resumeItemListStart
            \resumeItem{Designed and implemented RESTful APIs for user authentication, course management, and content delivery.}
            \resumeItem{Developed responsive UI components using React and Redux for an engaging learning experience.}
            \resumeItem{Integrated secure user authentication and authorization mechanisms.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{WAU-Net} \href{https://github.com/ahmed-fouad-lagha/MS-AGHairNet}{\faGithub} $|$ \emph{Python, TensorFlow, Keras, OpenCV}}{Jan. 2025 -- Jun. 2025}
          \resumeItemListStart
            \resumeItem{Engineered and trained a high-performance deep learning model for hair segmentation using Python, TensorFlow, and Keras, achieving state-of-the-art accuracy on benchmark datasets.}
            \resumeItem{Designed a comprehensive data augmentation pipeline, significantly improving model generalization and robustness across diverse image conditions.}
            \resumeItem{Evaluated model efficacy with rigorous metrics, attaining 95.37\% Dice coefficient for efficient real-time deployment.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Eötvös Loránd University (ELTE)}{Sep. 2025 -- Expected 2029}
      {Ph.D. in Informatics}{Budapest, Hungary}
    \resumeSubheading
      {University of Khenchela}{Sep. 2023 -- Jun. 2025}
      {M.Sc. in Artificial Intelligence, \textbf{GPA: 3.7/4.0}}{Khenchela, Algeria}
    \resumeSubheading
      {University of Khenchela}{Sep. 2020 -- Jun. 2023}
      {B.Sc. in Mathematics and Computer Science, \textbf{GPA: 3.9/4.0}}{Khenchela, Algeria}
  \resumeSubHeadingListEnd

\section{Certifications}
 \resumeItemListStart
    \resumeItem{\href{https://savanna.alxafrica.com/certificates/YEM9LC5BNm}{\textbf{AI Career Essentials (AiCE) certification}}, ALX South Africa ( \faCalendar* Jul. 2024 ) }
    \resumeItem{\href{https://www.datacamp.com/completed/statement-of-accomplishment/course/bb5dba576c82168b0fb58f231edd494cb2749eb0}{\textbf{Introduction to Deep Learning with PyTorch}}, Datacamp ( \faCalendar* Feb. 2025 ) }
    \resumeItem{\href{https://savanna.alxafrica.com/certificates/yNTLX6BYHR}{\textbf{ALX Software Engineering with a specialization in Back-end}}, ALX Africa ( \faCalendar* Feb. 2025 ) }
    \resumeItem{\href{https://www.coursera.org/account/accomplishments/verify/ZJWBYNRZ8WXK}{\textbf{Advanced Learning Algorithms}}, DeepLearning.AI, Stanford University ( \faCalendar* Apr. 2024 ) }
    \resumeItem{\href{https://www.coursera.org/account/accomplishments/records/UK73ZU6SNA29}{\textbf{Supervised Machine Learning}}, DeepLearning.AI, Stanford University ( \faCalendar* Apr. 2024 ) }
 \resumeItemListEnd

\section{Technical Skills}
  \textbf{Languages}{: Python, C/C++, Java, SQL, Bash, JavaScript}\\[3pt]
  \textbf{Databases}{: MySQL, SQLite, MongoDB}\\[3pt]
  \textbf{Data Science}{: Pandas, NumPy, Matplotlib, Seaborn}\\[3pt]
  \textbf{Machine Learning}{: PyTorch, TensorFlow, Keras, Scikit-learn, OpenCV}\\[3pt]
  \textbf{Web Development}{: HTML, CSS, Flask, Node.js}\\[3pt]
  \textbf{Tools}{: Git, Linux, CI/CD}\\[3pt]
  \textbf{Privacy-Preserving ML}{: Federated Learning, Differential Privacy}
 
\section{Languages}
    \textbf{Arabic}{: Native} \hspace{2pt} $|$ \hspace{2pt} \textbf{English}{: Professional Proficiency} \hspace{2pt} $|$ \hspace{2pt} \textbf{French}{: Intermediate}

\end{document}
